{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-28 wacv_for_review.tex
More typos fixed, and grammar mistakes corrected

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_t}$, represents the target's pixel
coordinates and its velocity, $\mathbf{X_t} = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
size of rows and columns of the confidence map. 
%Alternatively one can
%also use the Euclidean distance of particles to the location of
%maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate, using the object tracking benchmark datasets, the
performance of the proposed algorithm {\it E}nKCF and its variants.
Particularly, we choose two publicly, available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this version, we would like to
have an object tracking algorithm that ``efficiently'' runs on an
embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that contains the
videos recorded from smart phones and typical cameras in perspective
view. Also, we tested the proposed algorithm on a temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
dataset. What we would like to evaluate using this modified dataset is
how robust the proposed algorithm is to the drastic motions of camera
and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
with deep features, on the UAV123 dataset to observe how much gain we
can achieve over hand-crafted features.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about $5\%$ better than ours in accuracy, but 10-20 times
slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
For the scale adaptation, {\it E}nKCF did fourth best in terms
of AUC for the success rate plot. It outperformed other high-speed trackers
 by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we did not
use the particle filter to evaluate which order would work best,
without any extra components. The method at the $2^{nd}$ column
flipped the order of deploying $R_{t}^{L}$ and $R_{t}^{S}$. The one at
the $3^{th}$ column removed $R_{t}^{S}$ and replaces with $R_{t}^{L}$
whereas the one at the $4^{th}$ column removes $R_{t}^{L}$. The
methods marked with ``*'' ran the filters on every frame in the listed
order. The methods at the $7^{th}$ and $8^{th}$ columns ran a
translation and a scale filter on every frame which is very similar to
the way the LCT tracker \cite{ma2015long} runs.\footnote{To be
  precise, the LCT tracker comes with a re-detection module for a
  long-term tracking.} In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
at every frame, but this combination decreases run-time performance to
317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every
frame where $R_{t}^{S}$ uses the translation estimated by $R_{t}^{L}$
to update translation and $R_{s}$ uses the final translation
estimation given by $R_{t}^{S}$ to update the scale. Table
\ref{table:Comparison_to_LCT} indeed showed that it is very useful to
deploy more than one KCF as long as the deployment order is optimal.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle large displacement of objects in successive frames due to object
and camera motion. Specifically, we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Also, we can observe the sensitivity of 
the state-of-the-art lower speed trackers to the video frame rate b
y running them on this downsampled dataset. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
fourth in AUC while running about 10 to 100 times faster than the top three trackers.

In the lower frame rate scenarios (10 fps), the ECO and CCOT's precision rates drop about
$10\%$ worse than the original frame rate scenarios. We believe that this is an indicator of
how good of a performance we can expect from these trackers on low-end hardware. The projected
frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
convention described in section~\ref{introduction}. In this case, it would be reasonable to expect these
trackers to perform drastically worse on such hardware whereas the {\it E}nKCF can still perform similarly
due to its real-time speed on a low-end hardware. Our observations are also supported by \cite{mueller2017context}
that evaluates the correlation filter-driven trackers at variable frame rates matching their operation rates.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from a CNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows DeepE{\it n}KCF's
performance on UAV123 dataset. Deep{\it E}nKCF outperformed the {\it
  E}nKCF with hand-crafted features by about $3\%$ to $5\%$ in
precision (20 px) and $2\%$ in success rates (AUC). The
\textit{conv224-VGG} setting performed slightly better than
\textit{conv222-VGG} in precision while achieving similar success rate
(AUC). This indicates that higher level feature abstraction works
better for the smaller ROIs. By using feature abstractions from the
VGGNet pre-trained on millions of images, we can better represent the
low level features of the object than hand-crafted features in
challenging cases such as low contrast ROIs. However, we believe that
the contribution of the deep features is limited by two factors: (1)
low spatial resolution in deeper layers and (2) lost targets due to
large target and camera motion in the UAV123 dataset.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel 
coordinates using the evolution of the target's motion observed over frames.
Two public datasets were used to evaluate the performance of the
proposed algorithm and it was found that, on average, the performance of the
proposed algorithm is better than other high-speed trackers over 5\%
on precision at 20 pixels and 10-20\% on AUC. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123. Finally, we encoded objects with deep
features to boost tracking performance by $5\%$ on embedded systems
with GPUs.

>>>>

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_t}$, represents the target's pixel
coordinates and its velocity, $\mathbf{X_t} = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and 
$N$ and $M$ represent the number of rows and columns of the confidence map. 
%Alternatively one can
%also use the Euclidean distance of particles to the location of
%maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed algorithm {\it E}nKCF and its variants 
using the object tracking benchmark datasets. Particularly, we choose two publicly available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos of 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first test the {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this version, our goal is to
have an object tracking algorithm that ``efficiently'' runs on an
embedded system, a drone, in ``high speed,'' $\ge 30$
fps. Given this goal, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that contains the
videos recorded from smart phones and typical cameras in perspective
view. Also, we tested the proposed algorithm on a temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
dataset. What we would like to evaluate using this modified dataset is
how robust the proposed algorithm is to the drastic motions of camera
and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
with deep convolutional features, on the UAV123 dataset to observe how much gain we
can achieve over the hand-crafted features.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high and low speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
originally uses deep convolutional features, however, for the sake of fair comparison, we employ fHoG
and color-naming features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows 
the results on the UAV123 dataset. The {\it  E}nKCF outperformed other high-speed trackers by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about $5\%$ better than ours in accuracy, but 10-20 times
slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
For the scale adaptation, {\it E}nKCF did fourth best in terms
of AUC for the success rate plot. It outperformed other high-speed trackers
 by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to comparison with other trackers, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we did not
use the particle filter to evaluate which order would work best
without any extra components. The method at the $2^{nd}$ column
flipped the order of deploying $R_{t}^{L}$ and $R_{t}^{S}$. The one at
the $3^{th}$ column removed $R_{t}^{S}$ and replaces with $R_{t}^{L}$
whereas the one at the $4^{th}$ column removes $R_{t}^{L}$. The
methods marked with ``*'' ran the filters on every frame in the listed
order. The trackers at the $7^{th}$ and $8^{th}$ columns ran a
translation and a scale filter on every frame which is similar to
the LCT tracker \cite{ma2015long}.\footnote{To be
  precise, the LCT tracker comes with a re-detection module for a
  long-term tracking.} In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve $4.26\%$ higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
at every frame, but this combination decreases run-time performance to
317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every
frame where $R_{t}^{S}$ uses the translation estimated by $R_{t}^{L}$
to update translation and $R_{s}$ uses the final translation
estimation given by $R_{t}^{S}$ to update the scale. Table
\ref{table:Comparison_to_LCT} indeed showed that it is very useful to
deploy more than one KCF as long as the deployment order is optimal.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle large displacement of objects in successive frames due to object
and camera motion. Specifically, we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF on the temporally downsampled version of the UAV123 dataset, called 
UAV123$\_$10fps dataset. The downsampling operation makes the already challenging original dataset, 
because of objects in fast motion and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Also, we can measure the sensitivity of 
the state-of-the-art lower speed trackers to the smaller video frame rates. 
Figure \ref{fig:UAV123_10fpsDATASET} compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
fourth in AUC while running about $10$ to $100$ times faster than the top three trackers.

On the lower frame rate dataset ($10$ fps), the ECO and CCOT's precision rates drop about
$10\%$ worse than the original dataset. We believe that this is an indicator of
how good of a performance can be expected from these trackers on a limited hardware. The projected
frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
convention described in section~\ref{introduction}. In this case, it would be reasonable to expect these
trackers to perform drastically worse on such hardware whereas the {\it E}nKCF can still perform similarly
due to its real-time speed on a low-end hardware. Our observations are also supported by \cite{mueller2017context}
that evaluates the correlation filter-driven trackers at variable frame rates matching their operation rates.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board low-end 
embedded system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. To further boost the tracking accuracy, we replace
the conventional features with deep convolutional features similar to \cite{ma2015hierarchical,
  danelljan2015convolutional}. However, this performance boost comes with the cost
  of running the {\it E}nKCF on an embedded system with GPUs.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows the DeepE{\it n}KCF's
performance on UAV123 dataset. Deep{\it E}nKCF outperformed the {\it
  E}nKCF with hand-crafted features by about $3\%$ to $5\%$ in
precision (20 px) and $2\%$ in success rates (AUC). The
\textit{conv224-VGG} setting performed slightly better than
\textit{conv222-VGG} in precision while achieving similar success rate
(AUC). This indicates that higher level feature abstraction works
better for the smaller ROIs. By using feature abstractions from the
VGGNet pre-trained on millions of images, we can better represent the
low level features of the object than hand-crafted features in
challenging cases such as low contrast ROIs. However, we believe that
the contribution of the deep features is limited by two factors: (1)
increased translational invariance in deeper layers and (2) lost targets due to
large target and camera motion in the UAV123 dataset.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that it efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter to smooth the transition between three
KCFs, especially the transition between the scale and large ROI translation filter. 
Two public datasets were used to evaluate the performance of the
proposed algorithm and it was found that, on average, the performance of the
proposed algorithm is better than other high-speed trackers over 5\%
on precision at 20 pixels and 10-20\% on AUC. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps) 
for UAV123. Such operation rate tracker can potentially run at real-time
on a low-end embedded system. Finally, we encoded objects with deep
features to boost tracking performance by $5\%$ on embedded systems
with GPUs.
